---
title: "Dates and Times"
subtitle: "Maria C. Ramos"
author: ""
institute: "Cohort 4: R4DS"
date: "04/14/2021"
output:
  xaringan::moon_reader:
    seal: FALSE
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
editor_options: 
  chunk_output_type: inline
---
class: middle, center, middle

# Dates & Times 

<br><br>.large[Maria C. Ramos| Cohort 4: R4DS | 14 Apr 2021]

<br><br><br>`r icon::fa("link")`.large[mariacramos.com]
<br><br>`r icon::fa("twitter")`.large[@mariacramosf]
---
class: middle, center, center
```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(fig.retina = 3, warning = FALSE, message = FALSE)
library(tidyverse)
```
# Ice Breaker



---
# Outline

* Time Spans 
 
 + Durations
 + Periods
 + Intervals

* Time zones
---

# Durations 

.center[**exact number of seconds**]

Useful to get the difference between two dates

```{r}
library(lubridate)
my_time_diff <- today() - ymd(20210413)
my_time_diff
```

```{r}
as.duration(my_time_diff)#<<
```

---
# Duration Constructors

.pull-left[
```{r}
dseconds(1)
dminutes(1)
dhours(1)
```
]

.pull-right[
```{r}
ddays(1)
dweeks(1)
dyears(1)
```
]

---
# Duration Constructors


```{r}
dseconds(c(1, 15))
dminutes(0:5)
aux <- c(1,3,5,6)
dhours(aux)
```

---
# Duration Operations

```{r}
dseconds(15)*2
dseconds(15)+3
dyears(1)+dweeks(4)+ddays(7)
```

---
# Duration Drawbacks

Be careful with "human" times
```{r}
one_pm <- ymd_hms("2016-03-12 13:00:00", tz = "America/New_York")

one_pm

one_pm + ddays(1)
```

---
# Periods

.center[**Work with "human" times**]

---
# Period Constructors 

.pull-left[
```{r}
seconds(1)
minutes(1)
hours(1)
```
]

.pull-right[
```{r}
days(1)
weeks(1)
months(1)
years(1)
```
]
---
# Period Operations

```{r}

days(5)+1

days(5)*5

days(28)+ hours(24) + minutes(30)
```

---
# Period Operations

```{r}
one_pm <- ymd_hms("2016-03-12 13:00:00", tz = "America/New_York")

one_pm

one_pm + days(1)
```

---
# Intervals

.center[**Have a starting and ending point**]

```{r}
years(1)/days(1)
```

```{r}
next_year <- today() + years(1)
(today() %--% next_year)
(today() %--% next_year) / ddays(1)
```

---
# Intervals

```{r}
ymd(20210413) %--% ymd(20210412)
```

---
# Time zones

Get your time zone
```{r}
Sys.timezone()
```

---
# Time zones 
Get a complete list of time zone names

```{r}
head(OlsonNames(), n = 35)
```

---
# Time zones 

```{r}
(x1 <- ymd_hms("2015-06-01 12:00:00", tz = "America/New_York"))
(x2 <- ymd_hms("2015-06-01 18:00:00", tz = "Europe/Copenhagen"))
(x3 <- ymd_hms("2015-06-02 04:00:00", tz = "Pacific/Auckland"))

```

```{r}
x4 <- c(x1, x2, x3)
x4
```

---
# Changing Time Zones

1) Change only the display
```{r}

x4a <- with_tz(x4, tzone = "Australia/Lord_Howe")#<<
x4a
x4a - x4

```

---
# Changing Time Zones

2) Change the instant in time

```{r}
x4b <- force_tz(x4, tzone = "Australia/Lord_Howe") #<<
x4b
x4b - x4
```

---
class: center, middle

# Thanks!

Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).
